\documentclass[12pt]{book}

\begin{document}
\title{Snödroppe}
\author{Andi S.}
\date{November, 2020}
\maketitle

\chapter{They Walk the Same}

Buzz buzz... it was that time again: playtime. What adventures await today? Are they the same as yesterday? When even was yesterday? Time is something we've long forgotten in here. Markus was thinking hard about today's game. He wouldn't dare lose his chocolate chip cookies to Jake yet again. "Two left, then one right, and attack from the rear" he said to himself. It has to work, why wouldn't it?

"Are you ready for another butt whooping?" chanted Jake. "Eat my dirty socks!" replied Markus. The two finished lunch and handed their cookies to Billy. This was going to be intense. "You first" said Jake. Markus drew his cards then carefully placed them down. Jake took a moment to think then placed down his. "Call it" he said. Markus flipped over a card on the left. "Stegosaurus" he said. Jake followed by flipping over a card of Markus'. It was a Triceratops, oh no. "He takes you on like a mighty steer and crushes you". "Ugh" sighed Jake as he removed his card from the field.

The battle continued for a bit until Markus was down to his last card. It was time to pull the final move and attack from behind. "Say hello to my Tyrannosaurus Rex" he barked. "Not so fast"... Jake flipped over a surprise card. "Pterodactyl swarm comes in from the sky, your puny arms can't touch me". "No no not again!" gasped Markus. Billy called the game and started to hand the cookies to Jake when he was interrupted by a loud beep. "What was that?" said Billy.

The three ran over to the glass wall at the end of the room to watch. There were lights flashing on the other side and the sound of footsteps. "Oh no, oh no no no" Markus gasped very quietly. Left foot right foot left foot. The steps grew louder until out came a gray figure from around the corner. It was tall, bright, and was holding a large object--it was Frank. He continued walking: left foot right foot left foot--and stopped in front of the boys. He paused at a moments brief and then his neck twisted slowly in a grueling manner so the head faced them. "Huh" gasped Billy. "Stay calm" Markus grabbed Billy's arm firmly.

A moment later the head twisted back and he continued walking. They could hear a young girl speaking faintly on the other side: "I'm so happy, so very happy", "There will be no more rainy days, there will be no more skies of gray". A metal wall began closing down and covered the window. "Wait wait why can't we see her" said Billy. "She was chosen to move to the big kid's playroom" whispered Jake. "Only they are honored to see it". There was a moment of silence... then click, tick... BANG. A loud thud came from the floor. The metal wall reeled back up and Frank was gone along with the girl.

"Alright the action is over, I'd like to eat those cookies now" Jake said as he tapped Markus on the back. Billy and Jake began to walk back. Markus new what had really happened. He knew very well, and he knew he couldn't tell anyone. "They all walk the same" he said. "They always walk the same"...

\chapter{Doubts}

After playtime it was time to wind down. "Head to the west exit. You will now use the bathroom." screeched a static voice over the intercom. The intercom repeated again while the exit door raised open. The boys and the other kids formed a line and began to leave the room. "Two at a time" said the intercom. "Psst". "Psst" Markus felt someone poking his back. "Did you finally win?" said Neil. Markus turned around and gasped with a short "No!". "Ah that stinks. You'll get him next time." Neil replied. Jake was standing in front of the two and had chuckled with a contempt smile on his face.

Two by two the children took turns using the bathroom. Billy was holding his legs tightly "Come on I can't hold it much longer". Jake laughed for a moment then replied "You are like a lemon ready to be squeezed". A moment later the intercom shouted "Next!" as Jake and Billy went into the bathroom. This was no ordinary bathroom: it was huge yet largely empty--with only two stalls sitting in the back corner. Markus was looking up at the ceiling corner focusing hard. "What is it?" said Neil. Markus looked back down "Oh nothing..." he sighed.

Jake and Billy exited the bathroom and waited in the other line for bed. "Our turn" said Neil. The two entered and Neil went into one of the stalls. Meanwhile Markus stood by the sink and puzzled. Neil finished and headed towards him "You didn't have to go?" he said. "Not really" replied Markus. "There's something on my mind". "I think something is off here. Like, why is this bathroom so big?" he gasped and turned towards Neil. "Maybe the architect just overestimated the size of things" he responded. "That shiny eye... I feel like it's watching me. Like it knows me" Markus said quietly. The two finished up and headed out.

"Ah whatever try not to think to much" said Neil. A man with a gray uniform stood in front of the line. There was a smudged badge on the shirt which read "Lynn". "I'll talk later Markus" Neil said as he followed the man. Markus stood for a moment until the man returned. "Come" said the man in a mechanical tone. Markus began to follow him down the hall. "Left foot right foot left foot" Markus was saying to himself. They passed many doors until finally stopping. The man faced the door and pressed his hand against the black pad next to it.

The door opened up and the man walked away. Markus went into the room as the door closed behind him. The room was small, cold, and all gray. It felt so bland, but he made the best of it. There was a small bed with a book next to it and in the corner a stuffed Tyrannosaurus Rex. He went over to the corner and set down his cards next to the stuffed animal. "Maybe next time buddy" he said while tearing up and hugging it. He then lied down in bed and closed his eyes for a moment. It began to smell a little sweet.

Markus was drifting off until the air hastily grew bitter. He quickly got out of bed and lifted up the mattress. He dug his fingers into a small tear and pulled out a piece of paper. "Oh where is it, where is it" he said panting. He finally found it and pulled out a small pencil. He quickly made a marking on the paper then put it back into the mattress. In a flash of a moment he lied down and had fallen asleep.

\chapter{Ring Ring}

Time went on seamlessly, hours became days, days became weeks. Markus was keeping track and became increasingly anxious as each day passed. "One two three four one two three..." Markus was saying slowly to himself. "Alright now pick a card any card" Neil said. Billy pointed towards a card in the middle and then Neil shuffled it in with six cards in his other hand. He then drew one card from the pile and put it back into the deck and handed the other five cards to Billy. "Your card is gone" he said. Billy studied the cards very closely then gasped with a short sigh. "How do you keep doing this?". "A magician never reveals the secret" he winked.

Billy walked away to go see what Jake was doing meanwhile Markus kept puzzling. "Hey Neil" he said. "Can I show you something?". Neil was putting his cards away "Sure, what is it?". Markus was staring off into the distance and pointed his finger, "Look" he said. He pointed at Frank, who was walking around behind the glass wall. "Look very closely" he said. They both watched for a few minutes and nothing seemed to happen. Markus kept looking away at the clock on the ceiling and looking back. "I don't notice anything" Neil said. Frank continued walking down the hall and around the corner. Markus kept watching the clock and at the minute change he looked back and said "Now".

Frank stopped in front of the alarm bell down the hall and started twitching. A few seconds later he resumed walking. "Did you see that?" said Markus. "Frank is just walking around as usual, what is it?" Neil replied. He grabbed Neil's arm and they walked away towards the end of the room out of sight from the other children. "At the same time, every day, at the same spot, he does that." Markus said. "Doesn't that seem strange? Do you not think something is wrong here?" They both stood quietly for a minute.

"That same spot... why does he twitch when he passes it?" Markus said again. "Yeah, that is really weird" Neil replied. "It's always at the bell, it has to do something with that bell, I think" Markus said very quietly. Markus stared at Neil for a moment and wondered if he was thinking of the same thing. The bell rang and the intercom announced moments later that it would be time to eat soon. The two walked back from around the corner and went to find Billy and Jake.

"Ah soup again" grunted Billy as he sat down at the table joining the other three. "You complain to much" said Jake. The four ate their lunch as usual, there were no cookies today as those were quite rare. Billy was talking about Neil's card tricks. "I wish you'd show me how you did that already" he said to Neil. "I will one day" he replied back laughing. "I will show you one trick" he said. He pulled out his cards and begin to shuffle them. He handed some of them to Billy and slowly described each step.

Meanwhile Jake and Markus were talking. "You ready for me to whoop your butt again next week?" Jake had said. "Anything goes, don't be too cocky" Markus replied. "So look" he said to Jake. "I have a big favor to ask of you". Jake was finishing up the last slivers of his soup. "A favor, well I don't know about that..." he said with a contempt look on his face. "Look this is important Jake". Jake put down his spoon and laughed. "You like to draw and color right? Aren't you good at it?" "Maybe I am good at it, if I had cookies" Jake replied. "You can have my cookies for a month" said Markus. "I need you to draw me something... I need a picture of an alarm bell".

\chapter{The Mystery}

Another day passed and things seemed as usual. The boys were talking and Neil was showing off a card trick as always. "You sure are quite the show" said Jake, who looked back down to continue drawing. "Tricks are just as magical as the illusion" Neil replied. Markus kept staring over Jake's shoulder to see the progress. "Hold your horses Marko I'm not done yet" Jake said. "What do you need this stupid picture for anyway?" he asked. Markus hesitated for a moment then sighed "You will see soon enough". "Well it better be worth every cookie you're gonna be giving me!" Jake laughed.

Markus went to go walk around while Jake was finishing up. He stood by the glass wall and stared intensely at the bell for a moment. He then walked over to see the clock and what time it was. Neil finished showing Billy a trick then walked over to Markus. "So is this gonna work" Neil whispered into Markus' ear. Markus sighed and looked down for a moment. He then looked back up "It has to" he said. "It has to because my time is running out" he hissed quietly. "What do you mean?" Neil said as he put his hand on Markus' back. "Look Neil, you're the only one I can trust with this..." Markus was interrupted by a slap on the back.

"I finished your stupid picture" Markus heard as he jumped around and saw Jake. "You scared the life out of me" Markus said. "Don't worry, next time I'll scare the wimpiness out of you" Jake chuckled. He handed the drawing over to Markus then walked away with Billy. Markus stood for a moment and studied the picture. "One month" he heard in the distance. "Yeah yeah I know" Markus turned his head and said quickly. "Are you ready for this?" he asked Neil. "I was born ready!" he replied.

The two waited around for awhile checking back at the clock every few moments. Finally it was time and Frank appeared around the corner. "This is it" said Markus. They stood by the middle of the glass wall and watched Frank take one step at a time. Markus was sweating slightly, "left foot right foot" was all he could think of. He clinched up his left fist and continued waiting. Right as Frank was about to pass the two boys he quickly held up the picture of the bell against the wall where Frank could see it.

Frank continued walking on by as usual, step after step. Markus tried moving the paper around but Frank didn't seem to notice. "Why didn't it do anything?" asked Neil. Markus gasped and took a deep breath and wiped the sweat off his palms. He then held the paper and looked at it again. "I don't know" he said. "It had to work, why didn't it work, why didn't it" he continued. "Maybe it really is nothing" Neil said as he patted Markus' back and walked away. Markus walked over to the end of the hall where the alarm bell was. Frank was already gone at this point.

"I don't get it" Markus said as he stared at the drawing. He looked up at the bell and back down a few times: they looked exactly the same. The bell was sitting on a plain cement wall with nothing around it. "What else could it be?" he said to himself. Moments later the bell rang and the intercom announced it was time for bed. The children lined up and begin exiting to use the bathroom. Two by two they walked down the hall towards their cells. Neil was standing behind Markus "So any ideas?" he asked tapping Markus on the shoulder. "I don't know" Markus replied. They continued moving forward in the line. "Maybe there's something we're not seeing, something you only see standing in that spot" Neil said.

\chapter{Coming}

Markus was thinking hard to himself "only from that spot" as the line continued to move forward. The intercom yelled "next!" and two more children went into the bathroom as Lynn walked away to guide another to their cell. Markus quickly popped out of line and ran down the hall, stopping at the bell. He looked back to see Neil giving him a thumbs up as he checked to make sure Lynn was still away. Markus looked all around high and low. He just couldn't find anything but cement walls and the lonely bell hung on them.

Markus continued to survey the premises for any clues and noticed a mirror hanging from the ceiling at the end of the hall. The mirror just reflected the wall and floor and didn't seem interesting. He turned around again and saw Neil turning his head back and forth. Neil then looked at Markus again and moved his fingers in a motion to signal to hurry up. Markus was standing in the right spot but he just couldn't see anything. He looked at the mirror again and then puzzled for a second. "That's it!" he whispered slowly.

Neil was moving his hands very fast now and silently mouthed words as he looked at Markus. Markus held up his finger then turned back at the mirror. He tried to make himself taller by standing on the tips of his toes. He could see more of the wall reflected on the mirror when he stood taller. "It's nothing but a stupid wall" he said to himself. Markus jumped up in the air and could see more of the the wall the higher he was.

After a moment Markus looked back up at the mirror and froze instantly. He saw a figure standing behind him: he saw a face. Markus begin sweating as he turned around to see Lynn standing there, big beady black eyes, standing there staring at him. Markus stared back for a moment and then he saw Lynn flinch. "Line!" Lynn said very firmly. He stepped forward to put his arms around Markus and carry him back to the line. As he picked Markus up, Markus looked at the mirror again and could see cracks from the wall being reflected in it.

As Lynn carried Markus back to line he tried really hard to memorize the cracks reflected in the mirror. Lynn set Markus down and the remaining children were escorted to their cells. Markus finished using the bathroom and then followed Lynn to his cell as usual. Lynn pressed his hand against the black pad and the cell door opened. Markus walked into the room and let out a deep sigh. He then turned around and saw that Lynn was still standing there by the door.

Lynn continued to stare at Markus for a few moments and then finally closed the door and walked away. Markus felt really tense at this point and lifted up his mattress to search for that paper. He found it and pulled it out along with a pen. He then closed his eyes and tried to remember what the cracks looked like. After a few seconds he quickly jotted down some squiggly lines and connected parts of them together. He then sat on his bed staring at the paper. "I know just what to do" he said as he put the paper away closing his eyes and falling asleep.

\chapter{A Meaning?}

Morning arose and the children were eating their first meal. After Neil's usual card trick, Markus interrupted "So guys, I think I'm on to something". He pulled out the paper and placed it down on the table. "Lines that look like they were drawn by a 4-year old?" Jake said chuckling. "No" sighed Markus, "I think it's some kind of pattern, I just don't know what". Neil looked closely at the paper then handed it to Billy. "So what is this for anyway?" Billy asked.

"I believe there's something wrong with Frank" Markus said quietly. "He seems to stop in the same spot every day for just a second, as if he's looking at something". "These lines appeared in the mirror exactly where he stops" Markus said as he finished up his food. "That's absolute non-sense" Jake said sternly. "Are you trying to lead us into some conspiracy theory?" He got up and walked away with his empty food tray. Billy set the paper back down.

"So what could these lines mean?" Markus asked. They sat at the table for a few minutes thinking, looking hard at the paper. "Well here looks kinda like a circle" Neil pointed out "and the middle has a hook that looks almost like a two". "Yeah but the right side is just a jumble of lines" Markus replied. "It doesn't look much like anything". After a few moments of staring at the paper Billy made a suggestion "Maybe it's not the lines themselves, but something within the lines".

Markus took the paper and started to trace the lines of it onto another paper. "Zero... two" he said. "Hmm, the next few lines could make a six or an eight" Neil interrupted. Markus erased parts of the line to reveal a six. Now for the last few lines. "This last part could be anything" Markus hesitated. He drew the lines from the missing part onto another paper. "Maybe we will just have to guess, maybe they don't form a number" Neil said as he looked closely again at the paper.

Billy butted in "Maybe it's some sort of symbol, instead of a number". Billy took a pencil and drew over some of the lines. "It looks like an upside down triangle with something on the top" he said as he handed the paper to Markus. Markus looked at it for a moment "Billy you are a genius you know that!" he said excitedly. "Zero, two, six, and then the triangle shaped thing". "Maybe this is what Frank is seeing in the mirror".

The boys put away their meal plates and Markus returned to the table. He began to draw out the numbers on a new piece of paper then the triangle at the end. Neil sat back down to join him. "You ready to put this to the test?" he asked Neil. "Only as ready as you are" he replied.

\chapter{Trust}

After awhile everyone was settled down and doing the usual: mostly reading books or playing cards. "What does it mean... what does it mean!?" Markus said to himself. He and Neil were waiting at the end of the room by the glass wall. "Who knows?" said Neil. He glanced at the paper Markus was holding then thought to himself. A secret code? House address? Birthday? "This is the moment of truth" he said putting his hand on Markus's back.

The two continued waiting for Frank to pass by at his usual time. Markus was slightly nervous and sweating just a little but knew he had to do it. Billy came over to watch them. "Almost" Markus said as he watched the clock on the ceiling. "Jake thinks you're crazy" said Billy. "Maybe I am" Markus said. "Only one way to find out". Another moment passed and they heard footsteps. It was time.

Frank appeared around the corner and begin his slow lifeless walk. Markus, Neil, and Billy waited further down. "Left foot right foot" Frank was getting closer and closer. Right as he was about to approach the boys Markus held up the paper to the glass window. Frank passed by and took a few more steps before coming to a dead halt. He stands there completely still for a moment. "Oh no what's happening?" Neil said. They stood there for a moment and Frank began to turn his head slowly to face them. He then began to walk backwards.

Markus paused in shock as he watched the inhuman movements. Frank continued to step backwards until he reached the door in the glass. His hand thrust upwards and onto the latch to open it. "Stay calm" Markus said as he held the paper down. Frank slowly lifted up the latch all while staring hard at the boys. Click... creak... the door opened and one foot stepped inside following the other. He then began taking steps towards the boys until stopping in front of them.

They stood there staring hard at each other for a moment. Then Frank held out his hand and grabbed Neil's arm. "Oh no" Markus said. He grabbed Neil's other arm and tried to pull him away but Frank pulled back and was just too strong. Frank then let out a loud inhuman scream and shook his head in many directions. "The paper Markus the paper!". Frank pulled Neil in and then put his other hand around Neil's neck. Markus quickly got the paper back out and held it up. "Hey look at this" he shouted towards Frank.

Frank shook Neil a little and then looked at the paper again and froze still. He stared long and hard at it while the boys were panicking and sweating. After a few moments he let go of Neil and walked back out of the room and continued on his normal walk. Neil was shaking and tearing up. Jake came over after hearing the commotion "See what your crazy idea did?" he shouted at Markus. He and Billy were hugging Neil and trying to comfort him. Markus stood there looking at them and then whispered to himself "That was close".

\chapter{Bed Time Story}

It was another long day but bed time came before they knew it. The children were being escorted to their cells and Markus to his. After getting to his cell Markus laid down in bed and kicked his shoes off. "I can't believe it" he said to himself. "My friend was almost taken away for good, and it's all my fault". Markus reached into his pocket and pulled out the paper and unfolded it "What does this stupid thing mean anyway?".

"Oh what's the point!" he crumpled up the paper and threw it at the wall. He then pulled the blanket over himself and closed his eyes. "Just another day, I'll sleep it away". Before long Markus was fast asleep. A little while later there was a loud bang and Markus awoke. He could hear it raining heavily outside. "Oh it's just the weather" he said softly. After a moment he heard footsteps outside his cell. "Huh" he jumped up and sat on the side of the bed.

"Thud thud thud thud" he heard again. It sounded like something was walking back and forth in the hall. Markus felt his heart racing as he just stared at the door. He heard the thuds again, this time it stopped around the door. "THUD THUD" he heard two loud thuds just outside the door. He froze up completely and gripped his blanket. He was sweating with tension awaiting for the worst. "THUD" Markus flinched and continued staring. He heard a creaking sound and watched as his door slowly opened.

As he waited a foot stepped inside, followed by another. It was dark and gloomy, he could tell someone was there but couldn't make out who it was. "Hello" Markus said softly. The door slowly closed and the figure moved slightly closer. Markus was boiling with fear and he stood up. The figure moved again and the lights came on. It was Frank. Markus gasped heavily and then froze as he stared him in the eyes. After a few moments Frank finally showed some kind of life. He opened his mouth then said quietly "I'm not going to hurt you".

Frank walked towards the bed and then sat down on the side "Sit down" he said softly. Markus sat down on the bed next to him. "I need to tell you something" said Frank. "Long ago there was a war, a devastating one in which I fought." "That paper you showed me earlier, do you have it?" he asked. "Y-y-y-yesss" Markus said nervously. He ran over to the wall and picked up the crumpled paper and unraveled it. He sat back down on the bed and handed it to Frank.

Frank took the paper and studied it. "This" he said. "0-2-6... that was the number of the faction I led, and that triangle was the symbol the army used". "We are in an old military prison" he said looking at Markus. "But why are we here?" Markus replied feeling a little more comforted. "It all started long before you were born". Frank put his hand on Markus's back.

\chapter{The War}

Frank began telling his story to Markus "They wanted a way to help children with learning disabilities" he said. "There was a breakthrough in neural transmitters, which would let complex information be sent over immediately to be absorbed into the brain". Markus interrupted "So like a way to have school without school?" "Sort of" Frank replied. "It was a smash hit and kids who struggled to understand basic learning were now becoming top students" Frank said.

He continued "They began asking adults to use them, telling them how they could possess copious amounts of knowledge so easily". "Pretty soon almost everyone had one inside them" he said. "Well they actually ended up working too good and could interfere with the brain's conscious thoughts". "People started acting weird" Frank gasped as Markus was listening with enthusiasm.

"The system used to update the transmitters was ran by artificial intelligence, and as it continued to evolve people continued acting stranger and stranger". There was more heavy rain and a loud crack of thunder outside. Markus shook and jumped up really quick. "The A.I. was mutating to think for itself, and using the brains of those with the devices as a source of power to fuel self aware thoughts." "Well pretty soon the problem became apparent and the laboratory running the A.I. was ordered to be destroyed" he finished.

Frank paused for a second and Markus was moving his thumbs. "So what happened next?" he asked as he looked over at Frank. "The laboratory was destroyed, but it was already too late" Frank sighed. "The A.I. had split itself up and hid in the brains of a few with transmitters". "It instructed them to gather to a secret supercomputer hidden in a military base, where they connected their brains to the computer to make the A.I. whole again."

"The A.I. then sent out signals to everyone with a transmitter to rage war against those without them." Frank continued the story. "Pretty soon everyone was either wiped out or had a transmitter put in them" "I was in one of the factions that fought against them" he said. "We fought but we just couldn't win, and we too fell to their wrath". "They took the few of us who remained here to this prison and put transmitters inside us. After that it took control of me" he finished.

"Wow" said Markus. "I can't believe that happened. So why don't I have a transmitter? What about everyone else?". Frank sighed "This is what I wanted to tell you, you are being harvested" he said. "The A.I. is creating children in laboratories then putting them in here to develop to a certain point. After which..." Markus interrupted "They kill us don't they?". Frank sighed again "No, they remove your brain and put it inside of a jar which is hooked up to the central computer. The A.I. is using the brains like processors, to gain more power and more thoughts".

Markus froze up for a second. "Earlier when you showed me that picture, it must have glitched the transmitter" Frank said. "It allowed me to regain control of my thoughts for a moment, being able to remember the war." "But the A.I. kicked back in and ordered me to destroy your friend, but when you showed me it again I was able to break out of the loop" he said. "Now I can think for myself again, and now I want to help you..." "You've got to get out of here, and I just might know the way" Frank said then got up and left the cell.

\end{document}
